Timely Object Recognition

### 2012-03-06 writeups/eccv12/evaluation.tex
post-final i think

Figure~\ref{fig:results_manual} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.

@@

Figure~\ref{fig:results_entropy} shows the performance of the polices with learned weights.
A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features.

>>>>

Figure~\ref{fig:results_manual} also shows the performance of our policy with the heuristic value function and two inference models: the MRF model and a simple fixed-order model that follows the priors.
We can see that due to the dataset bias, the fixed-order policy performs well at first (the person class is disproportionately likely to be in the image), but is overtaken by the proper inference model as execution goes on.

@@

Figure~\ref{fig:results_entropy} shows the performance of the polices with learned weights, comparing our two reward functions.
We found the entropy-based reward to work better than the AP-based reward.

A notable difference between the MRF inference model and the fixed-order model was in the weights learned: while the fixed-order model learned weights onto the bias feature only, the MRF inference model learned weights onto a mix of the entropy and probability features.
